---  
title: "scRNA-seq: QC Report"
author: "SysBioLab"
output: 
  html_document:
    toc: true
    toc_float: true
    df_print: paged
    fig_width: 12
---

<!-- Sergio Alías, 20230706 -->
<!-- Last modified 20230709 -->

<style type='text/css'>
    body .main-container {
        max-width: 90%;

    }

    .plot_real_size {
      overflow: scroll;
      max-height: 600px;
    }

    .plot_real_size img{
      max-width: none;
      max-height: none;
    }

    embed {
   
  }   
</style>

<style>
.dropdown-content {
  display: none;
}
Error in parse(text = x, srcfile = src) : <text>:4:1: unexpected '<'
.dropdown:hover .dropdown-content {
  display: block;
}
</style>

<style>
  .superbigimage{
      overflow-x:scroll;
      white-space: nowrap;
  }

  .superbigimage img{
     max-width: none;
  }


</style>

# `r name` of project `r experiment`

Report of quality of FASTQ files using FastQC and Cell Ranger

```{r setup, echo = FALSE}
library(patchwork)
library(ggplot2)

metric_df <- read.table(file = metrics, sep = '\t', header = TRUE)
```

<div class="superbigimage">
```{r length_before_trimming, eval=TRUE, results='asis', echo=FALSE}

cat("\n\n## **Length distribution before trimming**\n\n")

ggplot() +
  geom_bar(metric_df,
           mapping = aes(sample, initial_total_sequences, fill = sample),
           width = 0.5,
           color = "black",
           stat = "identity")


```
</div>