---  
title: "scRNA-seq: QC Report"
author: "SysBioLab"
output: 
  html_document:
    toc: true
    toc_float: true
    df_print: paged
    fig_width: 12
---

<!-- Sergio Alías, 20230706 -->
<!-- Last modified 20230710 -->

<style type='text/css'>
    body .main-container {
        max-width: 90%;

    }

    .plot_real_size {
      overflow: scroll;
      max-height: 600px;
    }

    .plot_real_size img{
      max-width: none;
      max-height: none;
    }

    embed {
   
  }   
</style>

<style>
.dropdown-content {
  display: none;
}
Error in parse(text = x, srcfile = src) : <text>:4:1: unexpected '<'
.dropdown:hover .dropdown-content {
  display: block;
}
</style>

<style>
  .superbigimage{
      overflow-x:scroll;
      white-space: nowrap;
  }

  .superbigimage img{
     max-width: none;
  }


</style>

# `r name` of project `r experiment`

Report of quality of FASTQ files using FastQC and Cell Ranger

```{r setup, echo = FALSE}
library(patchwork)
library(ggplot2)

metric_df <- read.table(file = metrics, sep = '\t', header = TRUE)
long_metric_df <- read.table(file = long_metrics, sep = '\t', header = FALSE)
```

<div class="superbigimage">
```{r initial_total_sequences, eval=TRUE, results='asis', echo=FALSE}

cat("\n\n## **Number of sequences**\n\n")

make_barplot(metric_df, "initial_total_sequences")

```
</div>

<div class="superbigimage">
```{r initial_read_max_length, eval=TRUE, results='asis', echo=FALSE}

cat("\n\n## **Read maximum length**\n\n")

make_barplot(metric_df, "initial_read_max_length")

```
</div>

<div class="superbigimage">
```{r initial_read_min_length, eval=TRUE, results='asis', echo=FALSE}

cat("\n\n## **Read minimum length**\n\n")

make_barplot(metric_df, "initial_read_min_length")

```
</div>

<div class="superbigimage">
```{r initial_gc, eval=TRUE, results='asis', echo=FALSE}

cat("\n\n## **GC content**\n\n")

make_barplot(metric_df, "initial_.gc")

```
</div>

<div class="superbigimage">
```{r quality_scores, eval=TRUE, results='asis', echo=FALSE}

cat("\n\n## **Quality scores for samples - lowest scores (min/10th decile) and weighted average**\n\n")

make_hplot(long_metric_df, 
           c("initial_mean_qual_per_base",
             "initial_min_qual_per_base_in_lower_quartile",
             "initial_min_qual_per_base_in_10th_decile", 
             "initial_weigthed_qual_per_sequence"))

```
</div>

<div class="superbigimage">
```{r initial_mean_indeterminations_per_base, eval=TRUE, results='asis', echo=FALSE}

cat("\n\n## **Mean indeterminations per base**\n\n")

make_barplot(metric_df, "initial_mean_indeterminations_per_base")

```
</div>

<div class="superbigimage">
```{r initial_weigthed_read_length, eval=TRUE, results='asis', echo=FALSE}

cat("\n\n## **Weigthed read length**\n\n")

make_barplot(metric_df, "initial_weigthed_read_length")

```
</div>