## Feature selection

<!-- Sergio Alías, 20230629 -->
<!-- Last modified 20230704 -->

```{r fsel_plot, echo = FALSE}

list_seu <- ensure_list(seu)

for (i in 1:length(list_seu)) {
  top10 <- head(VariableFeatures(list_seu[[i]]), 10)
  featsel1 <- VariableFeaturePlot(list_seu[[i]]) +
    theme(legend.position="top")
  featsel2 <- LabelPoints(plot = featsel1, points = top10, repel = TRUE) + 
    theme(legend.position="none")
  featsel1 + featsel2
}

```

```{r fsel_removal, echo = FALSE}
rm(list_seu)
```

<details>
<summary>**How to interpret**</summary>
<br>

High variable genes (HVGs) selected: **`r hvgs`**

In the feature selection step we calculate subset of features that exhibit high cell-to-cell variation in the dataset—they are highly expressed in some cells, and lowly expressed in others. Focusing on these genes in downstream analysis helps to highlight biological signal in single-cell datasets.<sup>1</sup>

*References:*

1. Brennecke, Philip, Simon Anders, Jong Kyoung Kim, Aleksandra A Kołodziejczyk, Xiuwei Zhang, Valentina Proserpio, Bianka Baying, et al. 2013. “Accounting for Technical Noise in Single-Cell Rna-Seq Experiments.” *Nature Methods* 10 (11): 1093–5.

</details>