## Marker gene selection

<!-- Sergio Alías, 20230928 -->
<!-- Last modified 20230928 -->

```{r marker_gene_setup, echo = FALSE}
  if (isTRUE(inherits(markers, "data.frame"))){
    markers <- list(markers)
  }
```

```{r marker_gene_table, echo = FALSE, results = 'asis'}

for (i in 1:length(markers)) {
  print(scroll_box(kable_styling(kbl(markers[[i]]),
                         bootstrap_options = c("striped",
                                               "hover")),
           width = "100%",
           height = "500px"
           ))
  cat("\n")
}
```

<details>
<summary>**How to interpret**</summary>
<br>

We find markers that define clusters via differential expression. The table has the following columns:

- **p_val**: P-value
- **avg_logFC**: Average differential expression (log fold-change).
- **pct.1**: Percentage of cells in the cluster where the gene is detected. Here we desire values close to 1.
- **pct.2**: Percentage of cells on average in all the other clusters where the gene is detected. Here we desire values close to 0.
- **p_val_adj**: Adjusted p-value based on Bonferroni correction.
- **cluster**: Cluster number.
- **gene**: Gene name.

</details>