---  
title: "scRNA-seq: Pre-processing Report"
author: "SysBioLab"
output: 
  html_document:
    toc: true
    toc_float: true
    df_print: paged
    fig_width: 12
---

<!-- Sergio Alías, 20230606 -->
<!-- Last modified 20230928 -->

<style type='text/css'>
    body .main-container {
        max-width: 90%;

    }

    .plot_real_size {
      overflow: scroll;
      max-height: 600px;
    }

    .plot_real_size img{
      max-width: none;
      max-height: none;
    }

    embed {
   
  }   
</style>

<style>
.dropdown-content {
  display: none;
}

.dropdown:hover .dropdown-content {
  display: block;
}
</style>

<style>
  .superbigimage{
      overflow-x:scroll;
      white-space: nowrap;
  }

  .superbigimage img{
     max-width: none;
  }


</style>

# `r name` of project `r experiment`

Report of single-cell pre-processing using Seurat

```{r setup, echo = FALSE}
library(ggplot2)
library(patchwork)
library(kableExtra)
```

```{r child="qc.Rmd", eval = TRUE}
```

```{r child="feature_selection.Rmd", eval = TRUE}
```

```{r child="clustering.Rmd", eval = TRUE}
```

```{r child="dimensionality_reduction.Rmd", eval = TRUE}
```

```{r child="marker_gene_selection.Rmd", eval = TRUE}
```

---

<details>
<summary>**Code references**</summary>
<br>

- [https://satijalab.org/seurat/](https://satijalab.org/seurat/)

- [https://nbisweden.github.io/workshop-scRNAseq/labs/compiled/seurat/seurat_01_qc.html](https://nbisweden.github.io/workshop-scRNAseq/labs/compiled/seurat/seurat_01_qc.html)

- [https://holab-hku.github.io/Fundamental-scRNA/downstream.html#standard-pre-processing-workflow](https://holab-hku.github.io/Fundamental-scRNA/downstream.html#standard-pre-processing-workflow)

- [https://www.singlecellcourse.org/single-cell-rna-seq-analysis-using-seurat.html#normalization-and-dimensionality-reduction](https://www.singlecellcourse.org/single-cell-rna-seq-analysis-using-seurat.html#normalization-and-dimensionality-reduction)

</details>

<details>
<summary>**Session Info**</summary>

```{r sessionInfo, echo = FALSE}
sessionInfo()
```

</details>